Figures

### 2019-02-07 figures/06_lulc_buffer_demo.Rmd
linting

llid <- dt$lagoslakeid[2]
ll_pnt <- st_coordinates(
  st_transform(
    query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", llid), 4326))
ll_lake <- st_transform(
  query_gis("LAGOS_NE_All_Lakes_4ha", "lagoslakeid", llid), 4326)
network <- extract_network(lon = ll_pnt[1], 
                                   lat = ll_pnt[2], 
                                   maxsteps = Inf)
network <- network[unlist(lapply(
  st_intersects(network, st_transform(ll_lake, st_crs(network))), 
  function(x) length(x) == 0)),]

>>>>

llid <- dt$lagoslakeid[2]
ll_pnt <- st_coordinates(
  st_transform(
    query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", llid), 4326))
ll_lake <- st_transform(
  query_gis("LAGOS_NE_All_Lakes_4ha", "lagoslakeid", llid), 4326)
network <- extract_network(lon = ll_pnt[1], 
                                   lat = ll_pnt[2], 
                                   maxsteps = Inf, 
                           buffer_dist = units::as_units(5, "km"),
                           quiet = TRUE)
network <- network[unlist(lapply(
  st_intersects(network, st_transform(ll_lake, st_crs(network))), 
  function(x) length(x) == 0)),]
